A Formalisation of Sturm's theorem in \isabellehol

### 2013-11-27 paper/paper.tex
Tuned paper

\begin{document}
\maketitle
\tableofcontents
\newpage
\parindent0mm

@@

This paper will give a detailed proof that closely follows the structure of the formal proof in \isabellehol, but omits the proofs for basic lemmas about analysis and polynomials.\\

@@

\section{Notation}
\label{sec:notation}
In our the following proofs, we will use the following notation and terminology:
\begin{itemize}
\item $\RR[X]$ denotes the set of all polynomials with real coefficients.
\item $P'$ denotes the derivative of a polynomial $P\in\RR[X]$.
\item Some property holds in a neighbourhood of some $x_0\in\RR$ if there exists an $\epsilon > 0$ such that the property holds for all $x\in (x_0-\epsilon;x_0+\epsilon)\setminus\{x_0\}$. Note that it does not have to hold \emph{at} $x_0$ \emph{itself}.
\item $\mathrm{lc}(P)$ denotes the leading coefficient of a polynomial $P$.
\end{itemize}

>>>>

\begin{document}
\maketitle

\begin{abstract}
Sturm sequences are a sequence of polynomials with certain properties that, as shown by Sturm's theorem, can be used to determine the number of roots of a real polynomial in a given interval. In this project, Sturm's theorem and a number of me\-thods to construct Sturm sequences have been formalised in Isabelle\slash HOL. Buil\-ding upon this, an Isabelle\slash HOL proof method was then implemented to prove statements about the number of roots of a real polynomial and related properties.
\end{abstract}\vskip10mm

\tableofcontents
\newpage
\parindent0mm

@@

This paper will give a detailed account of the formalisation, including a very explicit proof that closely follows the structure of the formal proof in \isabellehol, but omits the proofs for basic lemmas about analysis and polynomials.\\

@@

\section{Notation}
\label{sec:notation}
In our the following proofs, we will use the following notation and terminology:
\begin{itemize}
\item $\RR[X]$ denotes the set of all polynomials with real coefficients.
\item $P'$ denotes the derivative of a polynomial $P\in\RR[X]$.
\item Some property holds in a neighbourhood of some $x_0\in\RR$ if there exists an $\epsilon > 0$ such that the property holds for all $x\in (x_0-\epsilon;x_0+\epsilon)\setminus\{x_0\}$. Note that it does \emph{not} have to hold \emph{at} $x_0$ \emph{itself}.
\item $\mathrm{lc}(P)$ denotes the leading coefficient of a polynomial $P$.
\end{itemize}
